Letter: Performance analysis of \\ high-resolution ice sheet simulations

### 2022-06-28 paper/perfmod.tex
attempt a final paragraph

FIXME The real promise of multigrid methods for the implicit, coupled geometry-update plus velocity solution problems; large constants are acceptable if $\beta,\gamma$ are less than 2, for example.  Specifically $\gamma < 1$ might be regarded as the goal of the next decades of research on numerical ice sheet models using Stokes dynamics.  However, this aspiration is long-term because work is barely started on it.

>>>>

The real promise of near-optimal methods is revealed when implicit, coupled mass/momentum solvers are considered.  That is, if a multigrid method can be designed which yields $\beta\approx 0$ for SIA models or $\gamma\approx 0$ for Stokes models then numerical ice sheet modeling tools will be qualitatively faster for many tasks.  Large constants would be acceptable if $\beta,\gamma$ are small.  Specifically, and more modestly, a $\gamma < 1$ implicit, essentially unconditionally-stable, Stokes time-stepping method might be regarded as an appropriate goal for the next decades of research on numerical ice sheet models.  Such a numerical ice sheet model would scale with resolution as well as current explicit SIA models, at $O(\Delta x^{-4})$ rate or better, and yet avoid shallow approximations.  In fact the same applies to the construction of capable higher-order or other membrane-stress resolving solvers.   These aspirations are admittedly long-term because, to the author's knowledge, no progress has yet been made.
